---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# asciify

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/djnavarro/asciify.svg?branch=master)](https://travis-ci.org/djnavarro/asciify)
[![CRAN status](https://www.r-pkg.org/badges/version/asciify)](https://cran.r-project.org/package=asciify)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A package to create ASCII art from arbitrary images. This is a work in progress and probably doesn't have a purpose, but I'm finding it fun.

```{r install}
# devtools::install_github("djnavarro/asciify")
library("asciify")
```

The core function in the package is `ascii_map`, which takes a path to an image file as the input, and returns a tibble converting the image to a character map:

```{r, warning=FALSE}
bayes_img <- ascii_data("bayes.png")      # path to the bayes image
bayes_map <- ascii_map(file = bayes_img)  # construct ASCII map
bayes_map
```
In the code chunk above `ascii_data` is just a convenience function that returns the path to an image file that comes bundled with the package.

The tibble has three variables: `x` and `y` specify the location of a character on a grid, and `label` specifes what character is shown at that location. The package includes a simple plot function that returns a ggplot:
```{r plotting}
ascii_plot(bayes_map, charsize = 2)
```

There are a few other handy functions in the package. For instance, you can convert the tibble representation from `ascii_map` into grid of characters using `ascii_grid`, which returns a matrix:

```{r}
bayes_grid <- ascii_grid(bayes_map)
str(bayes_grid)
```

Once converted to this grid format, you can write it to text file using `ascii_text`

```{r}
#ascii_text(bayes_grid, file = "something.txt")
```

Finally, for no particularly sensible reasion, the package also allows you to write the result to an HTML file that produces a "digital rain" animation. 

```{r}
#ascii_rain(bayes_grid, file = "something.html")
```

